\documentclass[]{plushcv}
\usepackage{fancyhdr}
\usepackage{hyperref}
\RequirePackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

\namesection{}{AATIF IMRAN}{Data Scientist}
{\contactline{\href{https://www.linkedin.com/in/aatif-imran23
}{Aatif Imran}}{\href{mailto:aatifimran.ai@gmail.com
}{aatifimran.ai@gmail.com
}}{\href{tel:+91 6290787982}{+91 6290787982}}{\href{https://github.com/aatifimran}{aatifimran}}}
\vspace{5pt}
\hrule
\vspace{10pt}

\section{Summary}
Entry level Data Scientist who is keen to contribute to a cause. I am a young, organised and geeky individual whose desire to learn is endless.
Familiar with gathering, cleaning and organizing data for use by technical and non-technical personnel.

\section{Skills}
\subsection{Programming/ TOOLS}
\vspace{\topsep}
\begin{tightemize}
\item Python  \hspace{2.52cm} \textbullet{} Jupyter
\item MS Excel \hspace{2.17cm} \textbullet{} CSS
\item Javascript \hspace{2.0cm} \textbullet{} \LaTeX
\end{tightemize}

\subsection{Libraries/ Frameworks}
\vspace{\topsep}
\begin{tightemize}
\item Numpy \hspace{2.50cm} \textbullet{} Pandas
\item Matplotlib \hspace{2.02cm} \textbullet{}   SciPy
\item Scikit-learn  \hspace{1.80cm} \textbullet{} NLTK
\item Keras \hspace{2.72cm} \textbullet{} Tensorflow
\item MySQL \hspace{2.46cm} \textbullet{}   Tableau
\item Flask \hspace{2.78cm} \textbullet{}   PySpark
\end{tightemize}


\section{Experience}
\runsubsection{Wipro\hspace{0.0cm}  |} \hspace{-0.25cm}
\descript{Project Management Associate}
\location{Oct 2022 – Present | Hyderabad }
\begin{tightemize}
\item Reviewing Google Adverts account using AART Tool \textbf{3000+ high quality solutions} for High School Mathematics Problems.
\item In a single academic year achieved \textbf{1.5+ millions} views for the posted solutions.
\end{tightemize}

\runsubsection{Quizlet\hspace{0.0cm}  |} \hspace{-0.25cm}
\descript{Content Contributor and Moderator }
\location{Mar 2021 – Aug 2022 | Remote }
\begin{tightemize}
\item Led a team of \textbf{15 Expert Contributors} and moderated their \textbf{10000+} solutions.
\item Created \textbf{1200+ high quality solutions} for advanced level Mathematics, DS \& Algo Problems.
\end{tightemize}

\runsubsection{Slader\hspace{0.0cm}  |} \hspace{-0.25cm}
\descript{Content Contributor}
\location{Mar 2019 – Feb 2021 | Remote }
\begin{tightemize}
\item Created \textbf{3000+ high quality solutions} for High School Mathematics Problems.
\item In a single academic year achieved \textbf{1.5+ millions} views for the posted solutions.
\end{tightemize}

\section{ACCOMPLISHMENT}
\textbullet{} Qualified \textbf{NASSCOM} certification in Data Science \& AI Program approved by GoI \\
\textbullet{} Ranked among the top 1\% in \textbf{WBJEE} | 2015\\
\textbullet{} Qualified \textbf{NATA} conducted by Council of Architecture | 2015
\\
\textbullet{} Ranked among the top 30 students in the Entrance Test of Abhyanand \textbf{Super-30} | 2012

\section{Education} 
\subsection{Heritage Inst. of Tech.}
\descript{B.Tech (2019) Civil Engineering}
\location{6.7/10 CGPA}

\subsection{SAM Secondary School }
\descript{AISSCE (2014)}
\location{69.2 \%}
\subsection{DAV Cent Public School}
\descript{AISSE \ \ (2012)}
\location{9.4/10 CGPA}

\end{document}